Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-25 Paper/gammaRays.tex
Added reference to Observations from Intro
Added links to model, results and summary to Intro

	Finally, we stretch the high energy CDF by different factors, and compare it to the low energy CDF using the KS-test.
	If we require $2\sigma$-significant probability to exclude a particular stretching factor, then the stretching factor of $1$ (which means no stretching) is allowed for GRB 080916C and GRB 090510.
	For the other two bursts the stretching factor of 1 is, however, excluded.
	For GRB 090902B it should be smaller than 1, so the low energy light curve is stretched with respect to the high energy one (see fig. \ref{fig:grb090902B}).
	And for GRB 090926A even more significant deviation from the stretching factor of 1 is observed in the opposite direction.
	The high energy light curve of GRB 090926A is stretched with respect to the low energy one by a factor of at least 1.99 (see fig. \ref{fig:grb090926A}).
	All observed stretching factors are summarized in table \ref{tab:observationResults}.

@@

	Finally, our assumption is able to explain the non-trivial stretching factor of both GRB 090902B and GRB 090926A.
	Detailed computations will be described in the following sections, but you can see the main idea on figure \ref{fig:modelOverview}.
	The computations confirm that this qualitative picture is indeed correct.
	You can see a sample light curves on figure \ref{fig:sampleLightCurves}, and predicted distribution of stretching factors on figure \ref{fig:kappaDistribution}.

@@

\section{Model}

@@

\section{Results}

>>>>

	Finally, we stretch the high energy CDF by different factors, and compare it to the low energy CDF using the KS-test.
	If we require $2\sigma$-significant probability to exclude a particular stretching factor, then the stretching factor of $1$ (which means no stretching) is allowed for GRB 080916C and GRB 090510.
	For the other two bursts the stretching factor of 1 is, however, excluded.
	For GRB 090902B it should be smaller than 1, so the low energy light curve is stretched with respect to the high energy one (see fig. \ref{fig:grb090902B}).
	And for GRB 090926A even more significant deviation from the stretching factor of 1 is observed in the opposite direction.
	The high energy light curve of GRB 090926A is stretched with respect to the low energy one by a factor of at least 1.99 (see fig. \ref{fig:grb090926A}).
	All observed stretching factors are summarized in table \ref{tab:observationResults}, and the detailed procedure for computing them is described in section \ref{sec:observations} of the paper.

@@

	Finally, our assumption is able to explain the non-trivial stretching factor of both GRB 090902B and GRB 090926A.
	Detailed computations are described in section \ref{sec:model}, but you can see the main idea on figure \ref{fig:modelOverview}.
	Computations confirm that this qualitative picture is indeed correct.
	You can see a sample light curves on figure \ref{fig:sampleLightCurves}, and predicted distribution of stretching factors on figure \ref{fig:kappaDistribution}.

	Results of our study, including a few predictions of our model and a new method for estimating jet observation angles, are summarized in section \ref{sec:results}, and the caveats are discussed in section \ref{sec:summary}.

@@

\section{Model}
\label{sec:model}

@@

\section{Results}
\label{sec:results}
